Leadership across 59 traditional cultures: an exploratory analysis

### 2019-12-03 leadership_across_cultures_contexts.Rmd
Shortened title and moved synthesis to concluding remarks

---
title: "Leader functions and qualities across 59 cultures: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2
bibliography: Leader2.bib
csl: evolution-and-human-behavior.csl
---

@@

## Synthesis

In general, our results conform to the characteristics of leaders that are emphasized in the literature on the evolution of leadership and provide broad cross-cultural support for several influential theoretical predictions [for review, see @garfield_evolutionary_2019]. Leaders in the ethnographic record are portrayed as generally prosocial, and serve to resolve conflicts and organize cooperation. Leaders also receive material, social, and reproductive benefits. There is also a "dominant" style of leadership involving physical formidability, fear, and aggression.

@@

# Conclusion

>>>>

---
title: "Leadership across 59 traditional cultures: an exploratory analysis"
author: "Zachary H. Garfield, Kristen L. Syme, and Edward H. Hagen"
date: "4/25/2019"
output: 
  bookdown::html_document2
bibliography: Leader2.bib
csl: evolution-and-human-behavior.csl
---

@@

# Concluding remarks

Our results conform to the characteristics of leaders that are emphasized in the literature on the evolution of leadership and provide broad cross-cultural support for several influential theoretical predictions [for review, see @garfield_evolutionary_2019]. Leaders in the ethnographic record are portrayed as generally prosocial, and serve to resolve conflicts and organize cooperation. Leaders also receive material, social, and reproductive benefits. There is also a "dominant" style of leadership involving physical formidability, fear, and aggression.

@@
